Aquifer depletion exacerbates agricultural drought losses in the US High Plains

### 2023-08-31 Writing/NatureWater/2ndRoundRevision/replies/cover_letter.tex
Edits to cover letter.

Specifically, in our revised manuscript, we have made the following major changes based on the reviewers' comments, alongside several minor adjustments to wording and to correct spelling and grammatical errors:

\begin{itemize}
    \item Updated the main results section to include additional variables (e.g., soil characteristics, state fixed effects) to strengthen how we account for unobservable factors in our regression analyses.
    \item Added several new figures (Figure 2 and Figure 5) to more clearly highlight the non-linearity and statistical significance of declining saturated thickness on per-area crop yields (Figure 2) and overall crop productivity (Figure 5), which, combined with revised discussion of our results, we believe enable readers to gain deeper understanding of the significance of our findings. 
    \item Conduct rigorous statistical testing of our main findings, in particular to highlight the specific climate and aquifer conditions at which aquifer depletion has statistically robust and significant impacts on drought impacts and risks, including how these thresholds vary between corn and soybean.
    \item Strengthened the descriptions on the underlying theoretical and empirical evidence for causal links between crop yield, share of irrigated acres, and aquifer thickness, which are one of the main empirical findings from our paper.
    \item Added a series of four appendices to discuss in more details our methods, robustness checks, limitations imposed by underlying data. 
\end{itemize}

>>>>

The vast majority of the changes we made are minor. Some notable changes are the following:

\begin{itemize}
    \item Fix a coding error that was creating invalid observations for our regressions analysis of the share of irrigated acres. Consequently, our results changed slightly. Our main conclusions and qualitative results are robust and did not change. 
    \item We added histograms of aquifer thickness in Figure 3.
\end{itemize}
